### 2013-05-16 inst/examples/BUGS/step_ahead_plots.Rmd
Potential plots for visualizing uncertainty #44
Run builds on results from allen.md

```{r}
y <- numeric(Tobs)
y[1] = 4.5
for(t in 1:(Tobs-1))
    y[t+1] = z_g() * f(y[t], h=0, p=p)
```

@@

```{r}
df_post <- step_ahead_predictors(y)

ggplot(df_post) + geom_point(aes(time, stock)) + 
  geom_line(aes(time, value, col=variable, group=interaction(L1,variable)), alpha=.1) + 
  facet_wrap(~variable) + 
  scale_colour_manual(values=colorkey, guide = guide_legend(override.aes = list(alpha = 1)))

@@

```{r}
get_forecasts <- function(i, Tobs, h_i){

>>>>

```{r}
Tobs <- 8
y <- numeric(Tobs)
y[1] = 4.5
for(t in 1:(Tobs-1))
    y[t+1] = z_g() * f(y[t], h=0, p=p)
```

@@

```{r}
crash_data <- step_ahead_posteriors(y)

ggplot(crash_data) + geom_point(aes(time, stock)) + 
  geom_line(aes(time, value, col=variable, group=interaction(L1,variable)), alpha=.1) + 
  facet_wrap(~variable) + 
  scale_colour_manual(values=colorkey, guide = guide_legend(override.aes = list(alpha = 1)))

@@

```{r}
library(expm)
get_forecasts <- function(i, Tobs, h_i){
